---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EECovCensRd: Consistent parameter estimation with censored covariates in R

Marissa C. Ashner and Tanya P. Garcia

## Installation

You can install the development version of EECovCensRd from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("marissaashner/EECovCensRd")
```

## Data Generation 

To illustrate the functions in EECovCensRd, let's simulate a dataset for a sample of $n = 500$ observations under $(\sim 40\%)$ random right censoring. Specifically, 

- $X \sim $
- $C \sim $
- $Z \sim $
- $\epsilon \sim N(0,1)$
- $Y = X + Z + \epsilon$
- $W = \min(X, C)$
- $\Delta = I(X\leq C)$.


```{r}
library(CensCovMethods)

### Generate Data 
n = 500
r = 0.4
X = rnorm(n, 0, 1)
C = rnorm(n, 0, 1)
Z = rnorm(n, 0, 1)
e = rnorm(n, 0, 1)
Y = X + Z + e
W = pmin(X, C)
D = ifelse(X <= C, 1, 0)
data_sample = data.frame(Y, W, D, Z)
```

## Complete Case Analysis 

```{r}
cc_estimate = cc_censored(formula = Y ~ beta[1]*W + beta[2] + beta[3]*Z,
                          cens_ind = "D", 
                          data = data_sample, 
                          starting_vals = c(0,0,0), 
                          par_vec = "beta",
                          sandwich_se = TRUE)
```

## Inverse Probability Weighting 

```{r}
ipw_estimate = ipw_censored(formula = Y ~ beta[1]*W + beta[2] + beta[3]*Z,
                          cens_ind = "D", 
                          cens_name = "W",
                          data = data_sample, 
                          starting_vals = c(0,0,0), 
                          par_vec = "beta",
                          sandwich_se = TRUE,
                          weight_opt = "MVN", 
                          weights_cov = "Z", 
                          weights_threshold = 25,
                          weight_stabilize = "KM")
```

## Augmented Inverse Probability Weighting 

```{r}
# aipw_estimate = aipw_censored()
```

## Maximum Likelihood 

```{r}
# mle_estimate = mle_censored()
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
